Neural Network Language Models for Automatic Speech Recognition

### 2018-12-12 paper/paper.tex
paper: Add citations for nlg-eval and pytorch lm
paper: Make the images slightly bigger

\begin{figure}[!ht]
\includegraphics[width=0.7\columnwidth]{sr-eda-wikitext-train-words}
\includegraphics[width=0.7\columnwidth]{sr-eda-wikitext-valid-words}
\centering
\caption{Training and Validation words in the WikiText dataset}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.7\columnwidth]{sr-eda-wikitext-bigrams}
\includegraphics[width=0.7\columnwidth]{sr-eda-wikitext-trigrams}
\centering
\caption{Training set Bigrams and Trigrams in the WikiText dataset}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.7\columnwidth]{sr-eda-gigaword-train-words}
\includegraphics[width=0.7\columnwidth]{sr-eda-gigaword-valid-words}
\centering
\caption{Training and Validation words in the Gigaword dataset}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.7\columnwidth]{sr-eda-gigaword-bigrams}
\includegraphics[width=0.7\columnwidth]{sr-eda-gigaword-trigrams}
\centering
\caption{Bigrams and Trigrams words in the Gigaword training set}
\end{figure}

@@

@@

\begin{figure}[!ht]
\includegraphics[width=0.7\columnwidth]{sr-perf-by-model-architecture}
\centering
\caption{Validation Set Performance by Model Architecture on WikiText}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.7\columnwidth]{sr-perf-by-hidden-lstm}
\includegraphics[width=0.7\columnwidth]{sr-perf-by-hidden-gru}
\includegraphics[width=0.7\columnwidth]{sr-perf-by-hidden-rnn}
\centering
\caption{Validation Set Performance by number of Hidden Layers on WikiText}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.7\columnwidth]{sr-perf-by-hidden-units-lstm}
\includegraphics[width=0.7\columnwidth]{sr-perf-by-hidden-units-gru}
\includegraphics[width=0.7\columnwidth]{sr-perf-by-hidden-units-rnn}
\centering
\caption{Validation Set Performance by number of Hidden Units on WikiText}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.7\columnwidth]{sr-perf-by-dropout-lstm}
\includegraphics[width=0.7\columnwidth]{sr-perf-by-dropout-gru}
\includegraphics[width=0.7\columnwidth]{sr-perf-by-dropout-rnn}
\centering
\caption{Validation Set Performance by Dropout Probability on WikiText}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.7\columnwidth]{sr-perf-by-embedding-lstm}
\includegraphics[width=0.7\columnwidth]{sr-perf-by-embedding-gru}
\includegraphics[width=0.7\columnwidth]{sr-perf-by-embedding-rnn}
\centering
\caption{Validation Set Performance by Embedding Dimension on WikiText}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.7\columnwidth]{sr-perf-by-shortlist-lstm}
\includegraphics[width=0.7\columnwidth]{sr-perf-by-shortlist-gru}
\includegraphics[width=0.7\columnwidth]{sr-perf-by-shortlist-rnn}
\centering
\caption{Validation Set Performance by Shortlist Dimension on WikiText}
\end{figure}

>>>>

\begin{figure}[!ht]
\includegraphics[width=0.8\columnwidth]{sr-eda-wikitext-train-words}
\includegraphics[width=0.8\columnwidth]{sr-eda-wikitext-valid-words}
\centering
\caption{Training and Validation words in the WikiText dataset}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\columnwidth]{sr-eda-wikitext-bigrams}
\includegraphics[width=0.8\columnwidth]{sr-eda-wikitext-trigrams}
\centering
\caption{Training set Bigrams and Trigrams in the WikiText dataset}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\columnwidth]{sr-eda-gigaword-train-words}
\includegraphics[width=0.8\columnwidth]{sr-eda-gigaword-valid-words}
\centering
\caption{Training and Validation words in the Gigaword dataset}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\columnwidth]{sr-eda-gigaword-bigrams}
\includegraphics[width=0.8\columnwidth]{sr-eda-gigaword-trigrams}
\centering
\caption{Bigrams and Trigrams words in the Gigaword training set}
\end{figure}

@@

The actual models were implemented as an extension to the PyTorch
WikiText RNN Language Modelling Example \cite{pytorchlm}. Metrics were
evaluated using the NLG-Eval toolkit by Sharma and others \cite{nlgeval}.

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\columnwidth]{sr-perf-by-model-architecture}
\centering
\caption{Validation Set Performance by Model Architecture on WikiText}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\columnwidth]{sr-perf-by-hidden-lstm}
\includegraphics[width=0.8\columnwidth]{sr-perf-by-hidden-gru}
\includegraphics[width=0.8\columnwidth]{sr-perf-by-hidden-rnn}
\centering
\caption{Validation Set Performance by number of Hidden Layers on WikiText}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\columnwidth]{sr-perf-by-hidden-units-lstm}
\includegraphics[width=0.8\columnwidth]{sr-perf-by-hidden-units-gru}
\includegraphics[width=0.8\columnwidth]{sr-perf-by-hidden-units-rnn}
\centering
\caption{Validation Set Performance by number of Hidden Units on WikiText}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\columnwidth]{sr-perf-by-dropout-lstm}
\includegraphics[width=0.8\columnwidth]{sr-perf-by-dropout-gru}
\includegraphics[width=0.8\columnwidth]{sr-perf-by-dropout-rnn}
\centering
\caption{Validation Set Performance by Dropout Probability on WikiText}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\columnwidth]{sr-perf-by-embedding-lstm}
\includegraphics[width=0.8\columnwidth]{sr-perf-by-embedding-gru}
\includegraphics[width=0.8\columnwidth]{sr-perf-by-embedding-rnn}
\centering
\caption{Validation Set Performance by Embedding Dimension on WikiText}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.8\columnwidth]{sr-perf-by-shortlist-lstm}
\includegraphics[width=0.8\columnwidth]{sr-perf-by-shortlist-gru}
\includegraphics[width=0.8\columnwidth]{sr-perf-by-shortlist-rnn}
\centering
\caption{Validation Set Performance by Shortlist Dimension on WikiText}
\end{figure}
